Three 38 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-03-16 papers/ms.tex
update ms

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more likely than for
  gray points (see Section~\ref{subsec:members}).
  Kepler-1627 is in the outskirts of the $\delta$ Lyr cluster
  \citep{bouma_kep1627_2022}, which is centered at $\{ l, b\} \approx
  \{ 66^\circ, 12^\circ\}$.
  {\it Middle row}: Galactic positions.  The Sun is at $\{X, Y, Z\} =
  \{0, 0, 20.8\}$ pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  longitudinal tangential velocity versus galactic latitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest.
  There is a strong spatial and kinematic overlap between Kepler-1643
  and RSG-5 (magenta points; $\{ l, b\} \approx \{ 82^\circ,
  6^\circ\}$; $\{ X, Y, Z\} \approx \{-8070, 330, 50\} $ pc).  The
  local population of candidate young stars around KOI-7368 and
  KOI-7913 is more diffuse -- we call this region ``CH-2'' (lime green
  points).  The green and purple points are manually selected from the
  initial candidate population based on galactic position and
  tangential velocity.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

The first step is to select stars that are photometrically distinct
from the field star population based on Gaia EDR3 magnitudes $\{G,
G_{\rm RP}, G_{\rm BP}\}$, parallaxes and auxiliary reddening
estimates \citep{lallement_gaia-2mass_2019}.  This step yielded \npms\
stars, which are either  pre-main-sequence K and M dwarfs due to their
long contraction timescales, or massive stars near the zero-age main
sequence due to their rapid evolutionary timescales.  The second step
is to then perform in an unsupervised HDBScan clustering on this
photometrically-young population
\citep{campello_hierarchical_2015,mcinnes_hdbscan_2017}.  The specific
parameters we use in this clustering analysis are $\{ X, Y, Z, c v_b,
c v_{l^*} \} $, where $c$ is the size-velocity corrective factor,
which is taken as $c=6\,{\rm pc / km\,s}^{-1}$ to ensure that the
spatial and velocity scales have identical standard deviations.  As
input parameters, we set the minimum $\epsilon$ threshold past which
clusters cannot be fragmented as $25$ in units of parsecs, and $c$
\kms\ in units of velocity.  The minimum cluster size $N$ is set to
10, as is $k$, the parameter used to define the ``core distance''
density metric.  This unsupervised clustering in our case
yielded 8 distinct groups.
These groups are then used as the ``seed'' populations for the third
step, which is to search for objects that are spatially and
kinematically consistent with each of the groups, {\bf WORDING NEEDS
WORK FOR CLARITY at least as close to the 10$^{\rm th}$ nearest HDBSCAN-identified
member in space-velocity coordinates as the most peripheral
HDBSCAN-identified member}.
The latter step yields F, G, and K-type stars that are spatially and
kinematically close to the photometrically-young stars, but which
cannot be identified as young based on their positions in color versus
absolute magnitude.

The outcome of this analysis is shown in Figure~\ref{fig:XYZvtang}.
We computed positions in these plots assuming the \texttt{astropy
v4.0} coordinate standard \citep{astropy_2018}, which assumes that the
Sun is $8122$ pc from the galactic center.  It also assumes
the solar velocity with respect to the local standard of rest from \citet{schonrich_local_2010}.
The previously known $\delta$~Lyr\ cluster ($l,b=68^\circ,15^\circ$;
$v_{l'}, v_b=-4.5{\rm kms},-4{\rm kms}$) is visible, as is
RSG-5 ($l,b=83^\circ,6^\circ$, $v_{l'}, v_b=+5.5{\rm kms},-3.5{\rm
kms}$).  Most of the other subclusters, including CH-2, and those in
Cep-Cyg ($l,b=90^\circ,7^\circ$) and Cerberus
($l,b=48^\circ,18^\circ$) are too small or dispersed to have
previously been analyzed in great detail.

To enable a selection cut that filters out field-star contaminants, we
also compute a weight metric, defined such that the group member
with the smallest core distance has a weight of 1, the group member
with the greatest core distance has a weight of 0, and weights for the
other group members are linearly spaced between these two extremes.
For Figure~\ref{fig:XYZvtang}, we show 26{,}960 objects with weight
exceeding 0.02 as gray points, and overplot 7{,}560 objects with
weights exceeding 0.10 as black points.

% FIXME FIXME ANYTHING ELSE TO SAY?
{\bf TODO: describe final step: manual selection of RSG-5 and CH-2 populations}

>>>>

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points (see Section~\ref{subsec:members}).
  Kepler-1627 is in the outskirts of the $\delta$ Lyr cluster
  \citep{bouma_kep1627_2022}, which is centered at $\{ l, b\} \approx
  \{ 66^\circ, 12^\circ\}$.
  {\it Middle row}: Galactic positions.  The Sun is at $\{X, Y, Z\} =
  \{0, 0, 20.8\}$ pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  longitudinal tangential velocity versus galactic latitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest.
  There is a strong spatial and kinematic overlap between Kepler-1643
  and RSG-5 ($\{ l, b\} \approx \{ 82^\circ,
  6^\circ\}$; $\{ X, Y, Z\} \approx \{60, 330, 50\} $ pc).  The
  local population of candidate young stars around KOI-7368 and
  KOI-7913 is more diffuse -- we call this region ``CH-2'',
  and treat it with additional skepticism
  The {\bf interactive figure} enables overplotting the candidate
  cluster members.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

The first step is to select stars that are photometrically distinct
from the field star population based on Gaia EDR3 magnitudes $\{G,
G_{\rm RP}, G_{\rm BP}\}$, parallaxes and auxiliary reddening
estimates \citep{lallement_gaia-2mass_2019}.  This step yielded \npms\
stars, which are either  pre-main-sequence K and M dwarfs due to their
long contraction timescales, or massive stars near the zero-age main
sequence due to their rapid evolutionary timescales.

The second step is to then perform in an unsupervised HDBScan
clustering on the photometrically selected population
\citep{campello_hierarchical_2015,mcinnes_hdbscan_2017}.  The specific
parameters we use in this clustering analysis are $\{ X, Y, Z, c v_b,
c v_{l^*} \} $, where $c$ is the size-velocity corrective factor,
which is taken as $c=6\,{\rm pc / km\,s}^{-1}$ to ensure that the
spatial and velocity scales have identical standard deviations.
Positions are computed assuming the \texttt{astropy v4.0} coordinate
standard \citep{astropy_2018}, which places the Sun $8122$ pc from the
galactic center, and assumes the solar velocity with respect to the
local standard of rest from \citet{schonrich_local_2010}.  As input
parameters to HDBScan, we set the minimum $\epsilon$ threshold past
which clusters cannot be fragmented as $25$ parsecs in physical space,
and $c$ \kms\ in velocity.  The minimum cluster size $N$ is set to 10,
as is $k$, the parameter used to define the ``core distance'' density
metric.

This unsupervised clustering in our case yielded 8 distinct groups.
These groups are then used as the ``seed'' populations for the third
step, which is to search for objects that are spatially and
kinematically consistent with each of the groups, {\bf WORDING NEEDS
WORK FOR CLARITY at least as close to the 10$^{\rm th}$ nearest
HDBSCAN-identified member in space-velocity coordinates as the most
peripheral HDBSCAN-identified member}.  This third step yields F, G,
and K-type stars that are spatially and kinematically close to the
photometrically-young stars, but which cannot be identified as young
based on their positions in color versus absolute magnitude.

The outcome of from the analysis up to the point of the third step is
shown in Figure~\ref{fig:XYZvtang}.  
To enable a selection cut that filters out field-star contaminants, we
also compute a weight metric, defined such that the group member
with the smallest core distance has a weight of 1, the group member
with the greatest core distance has a weight of 0, and weights for the
other group members are linearly spaced between these two extremes.
In Figure~\ref{fig:XYZvtang}, we show 26{,}960 objects with weight
exceeding 0.02 as gray points, and overplot 7{,}560 objects with
weights exceeding 0.10 as black points.

The previously known $\delta$~Lyr\ cluster ($l,b=68^\circ,15^\circ$;
$v_{l'}, v_b=-4.5{\rm kms},-4{\rm kms}$) is visible, as is RSG-5
($l,b=83^\circ,6^\circ$, $v_{l'}, v_b=+5.5{\rm kms},-3.5{\rm kms}$).
Most of the other subclusters, including in Cep-Cyg
($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great
detail.

Finally, there is a final step.
This paper is actually about planets, not this insane stellar
population.
We cross-matched
our candidate Cep-Her member list against 
all known Kepler Objects of Interest, including known false positives
\citep{thompson_planetary_2018}.
This yields 32 matches, of which 5 are ``confirmed''
planets according to the NASA Exoplanet Archive.
A cursory inspection of the light curves and RoboVetter (CITE)
classifications for these objects quickly revealed whether they were
consistent with being members of a $\lesssim 10^8$ year old
population.
Four candidate cluster members remained after this inspection:
Kepler-1627, Kepler-1643, KOI-7368, and KOI-7913.

Figure~\ref{fig:XYZvtang}

CH-2:
X: 20 to 80
Y: 230 to 270
Z: 70 to 105
vb: -1.5 to 3.5 kms
vl: 1 to 6 kms

RSG-5:
X: 45 to 75
Y: 320 to 350
Z: 40 to 70
vl: 4 to 6 kms
vb: -3 to -4 kms
